Dynamic Walking and Whole-Body Motion Planning for Humanoid Robots: an Integrated Approach

### 2012-12-07 paper.tex
Fix comment about environment representation.

\textbf{Our constrained motion planner and the small-space
  controllability property can luckily still be used with different
  environment representations that might be more suited with
  perception systems. Extensions in that directions
  \cite{Nakhei4755945, Dang6100889} are currently under development to
  relax the a priori environment knowledge constraint and achieve
  reactive planning in unknown environments.}

>>>>

\textbf{Our constrained motion planner and the small-space
  controllability property can luckily still be used with different
  environment representations that might be more suited for perception
  systems. Extensions \cite{Nakhei4755945,DanLauLam2012} are currently
  under development to relax the a priori environment knowledge
  constraint and achieve reactive planning in unknown environments.}
